### 2025-08-17 correlation.qmd
20250817 - library statement

```{r}
library("petersenlab")
library("XICOR")
library("psych")
library("DescTools")
library("psych")
library("correlation")
library("GGally")
library("ggridges")
library("tidyverse")
```

>>>>

```{r}
library("petersenlab")
library("XICOR")
library("psych")
library("DescTools")
library("psych")
library("correlation")
library("effectsize")
library("GGally")
library("ggridges")
library("tidyverse")
```
